### 2020-08-18 proposals/white-paper/white-paper.tex
white-paper = preproposal

%@TheDoctorRAB
%Standard white paper/preproposal format when there is a page limit
%neup.bst designed to use numbered citations in order of appearance, short author list
\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough
\usepackage{xcolor} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{subfig}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}}
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{caption}
\captionsetup[table]{skip=0pt} %sets a space after table caption
\usepackage{times}
\usepackage{enumitem}
%\usepackage[labelfont=bf]{caption}

@@

@@

@@

\begin{table}[h!]
    \centering
    \caption{Timeframe for Execution of Proposed Project.}
    \begin{tabular}{|l|l|l|l|l|l|}
        \hline
        \textbf{Tasks} & \textbf{M} & \textbf{M} & \textbf{M} & \textbf{M} & \textbf{M} \\
        \hline
        Task I & & & & & \\
        \hline
        Task II & & & & & \\
        \hline
        Task III & & & & & \\
        \hline
    \end{tabular}
    \label{tab-timeframe}
\end{table}

@@

>>>>

%@TheDoctorRAB
%Standard white paper/preproposal format when there is a page limit
%neup.bst designed to use numbered citations in order of appearance, short author list
\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough
\usepackage{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{subfig}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}}
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{times}
\usepackage{enumitem}
%\usepackage[labelfont=bf]{caption}

\usepackage[singlelinecheck=false]{caption}
\captionsetup[table]{skip=0pt} %sets a space after table caption
\captionsetup[figure]{skip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format

\usepackage{wrapfig}
\setlength{\intextsep}{0.10mm}
\setlength{\columnsep}{0.10mm}

@@

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell

@@

\noindent\textbf{Motivation.}
\\

@@

\begin{table}[h!]
    \centering
    \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
    \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|}
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}& 
        \multicolumn{4}{|c|}{\textbf{Y1}}&
        \multicolumn{4}{|c|}{\textbf{Y2}}&
        \multicolumn{4}{|c|}{\textbf{Y3}}\\
        \cline{2-13}
        &
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}\\
        \hline
        I. & & & & & & & & & & & & \\
        \hline
        II. & & & & & & & & & & & & \\
        \hline
        III. & & & & & & & & & & & & \\
        \hline
        IV. & & & & & & & & & & & & \\
        \hline
        V. & & & & & & & & & & & & \\
        \hline
        VI. & & & & & & & & & & & & \\
        \hline
        VII. & & & & & & & & & & & & \\
        \hline
    \end{tabular}
    \label{tab-timeframe}
\end{table}

@@

%wrap figure around text
%move to wherever in the text 
%{l} fixes it on the left margin
%\begin{wrapfigure}{l}{0.x\textwidth}
%       \includegraphics[width=0.(x-2)\textwidth]{}
%    \caption{}
%    \label{fig-}
%\end{wrapfigure}
